Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-17 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

Lattice and digital sequences are not unique, and improved or alternate versions continue to be constructed.  Stephen Joe and Frances Kuo \cite{JoeKuo03,KuoJoe08a,SobolDirection} have proposed  Sobol' generator direction numbers, which are now widely used, but were not part of early LD sequence software.  Pierre L'Ecuyer and collaborators have created LatNetBuilder \cite{LatNet} to construct good lattice and polynomial lattice sequences based on user-defined criteria. During a lunch at MCQMC 2022, it was proposed that we  agree on a consistent format for storing the parameters that define good LD sequences so that they can be shared across software libraries.

Users computing solutions in comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, have convenient access to LD sequence generators.  However, most of these implementations in large libraries would benefit a wider menu of LD offerings, including custom generators from LatNetBuilder or other sources.  Some large environments such as  Dakota \cite{DakotaUsersManual} have quite limited LD generators and should expand their offerings. SAS facilitates flexible integration of third-party open-source software; see \url{https://www.sas.com/en_us/software/viya/open.html}. This presents opportunities for  developers of smaller libraries with more QMC features, like BRODA and QMCPy, to connect their libraries with larger software environments. An example of QMCPy connecting with other software is given in the next subsection.

>>>>

Lattice and digital sequences are not unique, and improved or alternate versions continue to be constructed.  Stephen Joe and Frances Kuo \cite{JoeKuo03,KuoJoe08a,SobolDirection} have proposed  Sobol' generator direction numbers, which are now widely used, but were not part of early LD sequence software.  Pierre L'Ecuyer and collaborators have created LatNetBuilder \cite{LatNet} to construct good lattice and polynomial lattice sequences based on user-defined criteria. During lunch at MCQMC 2022, it was proposed that we  agree on a consistent format for storing the parameters that define good LD sequences so that they can be shared across software libraries.

Users computing solutions in comprehensive software environments, such as NAG, MATLAB, R, SciPy, and TensorFlow, have convenient access to LD sequence generators.  However, most of these implementations in large libraries would benefit a wider menu of LD offerings, including custom generators from LatNetBuilder or other sources.  Some large environments such as  Dakota \cite{DakotaUsersManual} have quite limited LD generators and should expand their offerings. SAS facilitates flexible integration of third-party open-source software; see \url{https://www.sas.com/en_us/software/viya/open.html}
 This presents opportunities for  developers of smaller libraries with more QMC features, like BRODA and QMCPy, to connect their libraries with larger software environments. An example of QMCPy connecting with other software is given in the next subsection.
